### 2015-08-28 fundamentals/impl.tex
references sections for each confusing term in the intro. Fixes #125
removes 'bring into relief the difference between qa and validation' bit
fixes #127

\subsubsection{Regions, Institutions, and Facilities}

@@

\subsubsection{Resources and Materials}
% Resources, Materials (note isotope tracking, decay behavior)

@@

Validation, in contrast,  may be defined as the question,
``Is \Cyclus the correct tool?''
Since \Cyclus is alone in its class as an agent-based fuel cycle simulator, longitudinal
validation is not possible. Nonetheless, code-to-code comparisons with fuel cycle
simulators that use other modeling paradigms are underway
\cite{huff_extensions_2014}. However, such
exercises are more likely to bring into relief the differences between the modeling
paradigms than supply substantial \gls{QA} and validation.

Sections \ref{sec:qa-testing}-\ref{sec:qa-ci} discuss in greater detail the software
development components that comprise the \Cyclus verification strategy.
Each of these on its own is a valuable addition to \gls{QA} but it cannot be the
entire answer to the requirements imposed by \gls{NQA1}. Taken together and strictly
adhered to, they present a fortress to protect against poorly designed or otherwise undesirable code.

>>>>

\subsubsection{Regions, Institutions, and Facilities}
\label{sec:rif}

@@

\subsubsection{Resources and Materials}
\label{sec:mats}
% Resources, Materials (note isotope tracking, decay behavior)

@@

Validation, in contrast,  may be defined as the question,
``Is \Cyclus the correct tool?''
Since \Cyclus is alone in its class as an agent-based fuel cycle simulator, longitudinal
validation is not possible. Nonetheless, code-to-code comparisons with fuel cycle
simulators that use other modeling paradigms are underway
\cite{huff_extensions_2014}.

Sections \ref{sec:qa-testing}-\ref{sec:qa-ci} discuss in greater detail the software
development components that comprise the \Cyclus verification strategy, which 
allows the simulation kernel and physics models to be tested explicitly and 
separately.
Each of these approaches on its own is a valuable addition to \gls{QA} but it cannot be the
entire answer to the requirements imposed by \gls{NQA1}. Taken together and strictly
adhered to, they present a fortress to protect against poorly designed or otherwise undesirable code.
